### 2017-11-05 Draft2/Appending.Growth.tex
Add stuff
Tweaks

Let $\FuncWritesByGrow(n)$ denote the total number of writes made by $\FuncGrow$, and let $\VarNumItemsTail$ be the size of the tail. Consider that [make corollary] also holds true for growth arrays, so $\FuncGrow$ is called $|\VarGrowSeq|$ times. A buffer is appended to the tail every time except the first, so the size of the tail is
\begin{align*}
\VarNumItemsTail &= |\VarGrowSeq| - 1 = |\VarCapacitySeq| - 2 = \VarUseful
\end{align*}
Then the formula for $\FuncWritesByGrow(n)$ is simply $\hat{\FuncWrites}(\VarUseful)$, where $\hat{\FuncWrites}$ is the write cost function for dynamic arrays. Finally, adding the writes made by $\FuncAppend$, the formula for $\FuncWrites(n)$ is
\begin{align*}
\FuncWrites(n) = n + \hat{\FuncWrites}(\VarUseful)
\end{align*}

>>>>

Let $\FuncWritesByGrow(n)$ denote the total number of writes made by $\FuncGrow$, and let $\VarNumItemsTail$ be the size of the tail. Consider that [make corollary] also holds true for growth arrays, so $\FuncGrow$ is called $|\VarGrowSeq|$ times. A buffer is appended to the tail every time except the first, so the size of the tail is
\begin{align*}
\VarNumItemsTail &= |\VarGrowSeq| - 1 = |\VarCapacitySeq| - 2 = \VarUseful
\end{align*}
Then the formula for $\FuncWritesByGrow(n)$ is simply $\hat{\FuncWrites}(\VarUseful)$, where $\hat{\FuncWrites}$ denotes the write cost function for dynamic arrays. Finally, adding the writes made by $\FuncAppend$, the formula for $\FuncWrites(n)$ is
\begin{align*}
\FuncWrites(n) = n + \hat{\FuncWrites}(\VarUseful)
\end{align*}
% Todo: Make this a lemma.
Now, I approximate this expression using $\sim$. To do this, I will first need to find the big-O complexity of $\VarUseful$:
\begin{align*}
\VarUseful &= \max(\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil, 0)\\
\VarUseful &\sim \max(\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil, 0)\\
&\sim \lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil\\
&\sim \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity\\
&\sim \log_{\VarGrowthFactor} n
\end{align*}

By [lemma], $O(\VarUseful) = O(\log_{\VarGrowthFactor} n) = O(\log n)$.
